### 2011-01-26 Text/paper.tex
Repaired the quarter code for parallel version. Right now totally coincides with the serial version.

\section{Train simulation}
As far as the requirements for the grid are ``heavy'' we performed a bunch of simulations to
examine how the distance between bubbles influences on the thickness. For this purpose the
simulation was conducted on the grid 82x82x750. We examined different initialized distances between
bubbles. The initial lengths of bubbles were chosen as $300$, $350$, $400$, $450$, $500$, $550$
lattice units. Therefore, the corresponding initial distances between bubbles are
$450$,$400$,$350$,$300$,$250$ lattice units. On the steady state regime the distances become $386$,
$317$, $248$,$176$,$99$,$23$ lattice units. The corresponding capillary numbers calculated based on
the center bubble velocity are as follows $0.905$, $0.986$,$1.08$,$1.19$, $1.33$, $1.49$. The
calculated radiuses (diagonal radius equal to the axes radius) are as follows
$0.783$,$0.778$,$0.772$,$0.764$,$0.753$,$0.747$. Thus, one can see the great impact of the bubbles
on each other velocity for the given body force. However, in terms of the film thicknesses those
numbers look adequate. One can see the film thicknesses dependency on the capillary number for the
\citeauthor{heil-threedim} and bubble train simulations data in Fig. \ref{fig:capillaries:train}. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison_train.eps}
\caption{Some more information on representing \label{fig:capillaries:train}}
\end{figure}

>>>>

\section{Train simulation}
As far as the requirements for the grid are ``heavy'' we performed a bunch of simulations to
examine how the distance between bubbles influences on the thickness. For this purpose the
simulation was conducted on the grid 82x82x750. We examined different initialized distances between
bubbles. The initial lengths of bubbles were chosen as $300$, $350$, $400$, $450$, $500$, $550$
lattice units. Therefore, the corresponding initial distances between bubbles are
$450$,$400$,$350$,$300$,$250$ lattice units. On the steady state regime the distances become $386$,
$317$, $248$,$176$,$99$,$23$ lattice units. The corresponding capillary numbers calculated based on
the center bubble velocity are as follows $0.905$, $0.986$,$1.08$,$1.19$, $1.33$, $1.49$. The
calculated radiuses (diagonal radius equal to the axes radius) are as follows
$0.783$,$0.778$,$0.772$,$0.764$,$0.753$,$0.747$. Thus, one can see the great impact of the bubbles
on each other velocity for the given body force. However, in terms of the film thicknesses those
numbers look adequate. One can see the film thicknesses dependency on the capillary number for
simulations obtained by \citet{heil-threedim} and bubble train simulations data in Fig.
\ref{fig:capillaries:train}. One can see that the results are consistent and in a good agreement.
Therefore, though the bubble train mutual motion influences on the film thickness by increasing the
associated capillary number,  however, the film thickness is in accordance with the capillary
number correlation. Thus, the decrease of the numerical domain is quantified and can be used to
obtain the data. However, one should be cautious about the initialization, because the Poiseuille
flow initialization is deviated even further due to mutual motion of bubbles.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison_train.eps}
\caption{The comparison for the film thickness between \citet{heil-threedim} data and bubble train
simulations. Though, one can see that the decrease of the distance between bubbles causes the
increase in the associated capillary number, however, the correlation dependance between film
thickness and capillary number stays the same. This can help for simulations to reduce the
numerical domain. \label{fig:capillaries:train}}
\end{figure}
